Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-11-30 demystify.tex
updates

Grades generally do not matter much for CS PhD admission. PhD in CS is a research degree and doing well in undergrad courses does not necessarily mean you can do research (other factors such as research experiences, pubs, LoRs are more important).

Nonetheless, if you are from a well-known school, having good grades do help (not a lot though), e.g., adcom members often note details such as "good GPA from well-known school (\autoref{sec:ievaluate}). However if your school is not well-known, having top grades or rankings usually will not help because we cannot evaluate them (e.g., we don't know how hard it is to get a 4.0 or A's at your school). This can be an issue for students in many top international universities where the competition is so high that very good students can still have low rankings from these schools (and be overlooked by adcom).

>>>>

Compared to other factors such as LoRs (\autoref{sec:lor}) and research experiences (\autoref{sec:research-experience}), grades generally do not matter much for CS PhD admission. PhD in CS is a research degree and doing well in undergrad courses does not necessarily mean you can do research (other factors such as research experiences, pubs, LoRs are more important).  In fact, many CS faculty members themselves have bad grades in undergrad courses (and some were proud of that!).

Nonetheless, if you are from a well-known school (\autoref{sec:your-school}), having good grades do help (not a lot though), e.g., adcom members often note details such as "good GPA from well-known school (\autoref{sec:ievaluate}). However if your school is not well-known, having top grades or rankings usually will not help because we cannot evaluate them (e.g., we don't know how hard it is to get a 4.0 or A's at your school). This can be an issue for students in many top international universities where the competition is so high that very good students can still have low rankings from these schools (and be overlooked by adcom).
